---
title: "Exploring the Manifestation of Comorbid Symptoms in Chinese Adolescents with Depression"
shorttitle: "Clinical depression in Chinese adolescents"
author: "Annika Liu"
date: Jan,29,2024
---
# Assignment 11
```{r male depression level graph}
# I saved depression and anxiety levels for the later study, but I think it is a good chance to maybe see the scatter polt distribution for scores for both of the gender to gain a general picture for my hypothesis writing 
library(readxl)
library(ggplot2)
library(dplyr)

# read the mocked up data
file_path <- "mockedupdata.xlsx"
depression_long <- readxl::read_excel(file_path)

female_data <- depression_long %>% 
  filter(Gender == "Female")

female_data <- female_data %>%
  group_by(Depression_Score) %>%
  mutate(count = row_number()) %>%
  ungroup()

ggplot(female_data, aes(x = Depression_Score, y = count)) +
  geom_jitter(width = 0.2, shape = 1) +  
  labs(title = "Scatter Plot of Depression Score for Females", x = "Depression Score" , y = "Count") +
  theme_minimal()

# Filter out the data for males
male_data <- depression_long %>%
  filter(Gender == "Male") %>%
  group_by(Depression_Score) %>%
  mutate(count = row_number()) %>%
  ungroup()

# Create the scatter plot for males vs. depression 
ggplot(male_data, aes(x = Depression_Score , y = count)) +
  geom_jitter(width = 0.2, shape = 1) +  
  labs(title = "Scatter Plot of Depression Score for Males", x = "Depression Score", y = "Count") +
  theme_minimal()

```
# Assignment 10
```{r male depression level graph}
# install the necessary packages 
library(readxl)
library(ggplot2)
library(dplyr)

# read the mocked up data
file_path <- "mockedupdata.xlsx"
depression_long <- readxl::read_excel(file_path)

# chose the male group and selected level_types 
depression_long %>%
  filter(Gender == "Male" & Level_Types == "Depression") %>%
  ggplot(aes(x = Level_Measure)) +
    geom_bar() +
    theme_minimal() +
    labs(title = "Depression Level Measure Count for Males",
         x = "Level Measure",
         y = "Count")

```

```{r female depression level graph}
# install the necessary packages 
library(readxl)
library(ggplot2)
library(dplyr)

# read the mocked up data
file_path <- "mockedupdata.xlsx"
depression_long <- readxl::read_excel(file_path)

# create male depression level graph
male_histogram <- depression_long %>%
  filter(Gender == "Male" & Level_Types == "Depression") %>%
  ggplot(aes(x = Level_Measure)) +
    geom_histogram(stat = "count", fill = "blue", color = "black") +
    theme_minimal() +
    labs(title = "Depression Level Measure Distribution for Male",
         x = "Level Measure",
         y = "Count")

# creating female depression graph 
female_histogram <- depression_long %>%
  filter(Gender == "Female" & Level_Types == "Depression") %>%
  ggplot(aes(x = Level_Measure)) +
    geom_histogram(stat = "count", fill = "pink", color = "black") +
    theme_minimal() +
    labs(title = "Depression Level Measure Distribution for Female",
         x = "Level Measure",
         y = "Count")

# combine the graphs together 
# here I originally want to make them as one graph, but I think I failed to do so 
library(gridExtra)
grid.arrange(male_histogram, female_histogram, ncol = 2)

```

```{r read my data, include=FALSE}
# Load readr function
library(readr)

# find my pathway 
file_path <- "Depression.xlsx"
Depression.data <- readxl::read_excel(file_path)

str(Depression.data)
```
<!-- This is a tidy data seems like each column is a single variable, each row is a single observation, each cell is a single measurement -->
<!-- Sex, Age, SAS score/level, SDS score/level, and the following cormbid factors are necessary -->
```{r create-intermediate-dataset, echo=TRUE}
library(writexl)
library(dplyr)
library(readxl)

file_path <- "Depression.xlsx"
Depression.data <- readxl::read_excel(file_path)

# Using two dplyr functions
SASMild.data <- Depression.data %>%
  filter(`Anxiety Level (SAS)` == "Mild") %>%
  mutate(SASMean = mean(`Index Score (SAS)`, na.rm = TRUE))

# Specify the full path to the directory and the new Excel file
SASMild.data_file_path <- "SASMild_data.xlsx"

# Write the intermediate dataset to an Excel file
writexl::write_xlsx(SASMild.data, SASMild.data_file_path)

str(SASMild.data)
```
<!-- the excel seems like doing what I am asking -->

## source 
source("~/Desktop/R/AnnikaRepo, Homework/Hellowworld.R")

```{r, include=FALSE}
# object assignment
hello_world <- function(name = NULL) {
  # conditional statement: greeting based on if there is a name 
  message <- if (!is.null(name) && nchar(name) > 0) {
      # learning notes: !is.null(name) will be true if the name is not Null
      # nchar helps to to check whether the number of charecters in the string is 0
    paste0("Hello ", name, "!")
  } else {
    "Hello!"
  }
  print(message)
}

 # return value 1
hello_world("Annika")
 # return value 2
hello_world()
```

## markdowns practice 

### Headers <!-- I've have each of the three -->
### 1 unordered list
* List item 1
  * List item 2
    * List item 3
    
### 1 ordered list
1. List item 1
2. List item 2
   1.  a
3. List item 3
    
### Bold & italicized text
**BOLD**
*italics*

### linked URL
[example link](https://andiwodbajbdh.com)

### 1 HTML-style comment
<!-- comment comment comment -->

---
title             : "Exploring the Manifestation of Comorbid Symptoms in Chinese Adolescents with Depression"
shorttitle        : "Clinical depression in Chinese adolescents"
---
author: 
  - name          : "Annika Liu"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "xliu13@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

#source
source("Homework2.R")

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::


